---
title: "Exam Practice"
subtitle: 'BIOL 4994/4991'
author: "Ariana Negroni Santiago"
date: "Last compiled on `r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

```{r}
library(readxl)
library(dplyr)
```

## Practice data manupulation using Base R   
### Data from Cereal which includes:   
- name: Brand name of cereal  
- company: Manufacturer (G=General Mills, K=Kellog’s or Q=Quaker)   
- serving: Serving size (in cups)
- calories: Calories (per cup)
- fat: Fat (grams per cup)
- sodium: Sodium (mg per cup)
- carbs: Carbohydrates (grams per cup)
- fiber: Dietary Fiber (grams per cup)
- sugars: Sugars (grams per cup)
- protein: Protein (grams per cup)

#### Open data
```{r}
cereal <- read_excel("cereal.xlsx")
head(cereal)
```
## Five question:
1. Extract rows 1 to 10 from the cereal data frame. 
```{r}
rows10 <- subset(cereal[1:10, ])
rows10
```

2. Create a new data frame called Kelloggs that only contains rows where company == “K”. 
```{r}
Kelloggs <- subset(cereal, company == "K")
Kelloggs
```

3. From the cereal data, extract the names of all cereals that have more than 10 grams of sugar. 
```{r}
highsugar <- subset(cereal, sugars > 10)
highsugar
```

4. Find the mean calories of all cereals in the dataset. 
```{r}
calories <- cereal$calories
calories
mean(calories)
```

5. Count how many cereals have fiber greater than or equal to 2 grams 
```{r}
length(cereal$fiber[cereal$fiber>=2])
```

