---
title: "Midterm"
subtitle: 'BIOL 4994/4991'
author: "Ariana Negroni Santiago"
date: "Last compiled on `r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

## General Instructions 
- This is the Midterm-Exam. Each question is worth 20 points.    
- You must choose 5 out of the 6 questions to answer. Your maximum score is therefore 100 points.    
- It is highly recommended that all your results, including tables and outputs, are always visible in your R Markdown document.     
- The exam must be completed and submitted during class time, on Thursday, October 9, 2025, from 3:00 to 6:00 PM.    
- Use R and the tidyverse packages to answer all questions.    
- Work independently and make sure your code is reproducible.    

```{r, message=FALSE}
library(tidyverse)
library(dplyr)
library(aod)
```

```{r, message=FALSE}
msleep <- glimpse(msleep)
storms <- storms
lizards <- lizards
head(msleep)
head(storms)
head(lizards)
```

### Mammals sleep dataset (msleep)   
1. Use filter() to subset msleep to only animals who are awake for at least 12 hours of the day.
```{r, message=FALSE}
msleep %>%
  filter(awake >= 12)
```

2. Use mutate() to create a new column called percent_day_awake that gives the percentage of the day that each species spends awake. Use select() with everything() at the end to verify your calculation.
```{r, message=FALSE}
msleep %>%
  mutate(percent_day_awake = ((awake/24) * 100)) %>% 
  select(percent_day_awake, everything())
```

### Storm tracks data (storms)
4. Use filter() to subset storms to only storms with wind speeds greater than 50 knots, then use arrange() to sort by wind descending.
```{r, message=FALSE}
storms %>%
  filter(wind>50) %>% 
  arrange(desc(wind))
```

### A Comparison of Site Preferences of Two Species of Lizard (lizards)   
5. Determine which Site and Diameter combination has the highest total grahami.

```{r, message=FALSE}
lizards %>% 
  group_by(Site, Diameter) %>% 
  summarise(sum_grahami = sum(grahami)) %>% 
  arrange(desc(sum_grahami))
```

6. Identify which Time of day has the highest average opalinus count.


```{r, message=FALSE}
lizards %>% 
  group_by(Time) %>% 
  summarise(opalinus_ave = mean(opalinus)) %>% 
  arrange(desc(opalinus_ave))
```











