---
title: "R Tutorial 1"
subtitle: 'BIOL 4994/4991'
author: "Ariana Negroni Santiago"
date: "Last compiled on `r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

# Instructions 
- This assignment consists of 10 questions, each worth 10 points.
- Write your answers in R code chunks whenever applicable.
- Make sure your code runs without errors. Include comments if necessary.
- For questions about chunk options, experiment with the options and write down your observations.
- Submit the assignment on your personal webpages using the HTML file exported/knit from the .Rmd.
- Do not copy output screenshots unless requested.



### Assigning values
1. Create an object called height with the value 175. Print it. 

```{r}
height <- 175
height
```


### Simple math
2. Calculate the result of 25 * 4 - 10.

```{r}
25*4-10
```

### Using functions
3. Use the function sqrt() to calculate the square root of 81. 

```{r}
sqrt(81)
```

### Character objects
4. Assign the phrase “R is fun!” to an object called message. Print it. 

```{r}
message <- "R is fun!"
message
```

### Object manipulation
5. Create two objects a <- 10 and b <- 5. Calculate their sum and store it in c. 

```{r}
a <- 10
b <- 5
c <- a + b
c
```

### Logical comparison
6. Test whether 15 is greater than 20.

```{r}
15>20
```

### Checking classes
7. Check the class of the object "Hello World".

```{r}
class("Hello World")
```

### Code chunk options
8. Run the following code chunk:  
- Observe the warnings that appear.   
- Modify the chunk options to suppress warnings without changing the code itself.   
log(-1)  
## Warning in log(-1): NaNs produced  
## [1] NaN  

```{r, warning=FALSE}
log(-1)

```

### Code chunk options
9. Run the following code chunk: - Observe the messages that appear. 
Modify the chunk options to suppress messages without changing the code itself.   
# Load a package (may produce messages)  
library(dplyr)  
## Warning: package 'dplyr' was built under R version 4.4.3  
##   
## Attaching package: 'dplyr'  
## The following objects are masked from 'package:stats':  
##   
##     filter, lag  
## The following objects are masked from 'package:base':  
##   
##     intersect, setdiff, setequal, union   

```{r, message=FALSE}

library(dplyr)

```

### Help files
10. Use R’s help system to find out what the function mean() does.

```{r}
?mean()
```


### Sum
11.  Sum 5+10


```{r}
5+10
```

