---
title: "R Tutorial 3"
subtitle: 'BIOL 4994/4991'
author: "Ariana Negroni Santiago"
date: "Last compiled on `r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---
## Instructions:   
- This assignment consists of 10 questions, each worth 10 points.   
- Write your answers in R code chunks whenever applicable.   
- Make sure your code runs without errors. Include comments if necessary.   
- Always display at least 6 rows of output for each question using head(…, 6) or more, so you can clearly see the results in your HTML file.    
- For questions about chunk options, experiment with the options and write down your observations.   
- Submit the assignment on your personal webpages using the HTML file exported/knit from the .Rmd.    
- Do not copy output screenshots unless requested.   

### Install necessary packages (only run once if not installed). 

```{r}
# install.packages("gapminder")
# install.packages("dplyr")
library(dplyr)
library(gapminder)
data(gapminder)
head(gapminder)
```

### 1. What class is the gapminder dataset? 

```{r}
class('gapminder')
```

### 2. Filter a section of gapminder with a life expectancy smaller than 29. 

```{r}
gapminder %>%
  filter (lifeExp < 29)
```

### 3. Filter the dataset for the country Rwanda and for years greater than 1979. 

```{r}
rwanda <- gapminder %>%
  filter(country == "Rwanda", year > 1979)
rwanda
```

### 4. Create a new dataset from gapminder excluding the column gdpPercap. 

```{r}
newdataset <- gapminder %>% 
  select(-gdpPercap)
newdataset
```

### 5. Arrange the dataset in ascending order of lifeExp.

```{r}
lifeExp_asc <- gapminder %>% 
  arrange(lifeExp)
lifeExp_asc
```


### 6. Arrange the dataset in descending order of lifeExp.

```{r}
lifeExp_desc <- gapminder %>% 
  arrange(desc(lifeExp))
lifeExp_desc
```

### 7. Create a new dataset with only the columns year and lifeExp.

```{r}
newdataset_yearlifeexp <- gapminder %>% 
  select(year, lifeExp)
newdataset_yearlifeexp
```

### 8. Filter the dataset for the country Cambodia and show only the columns year and lifeExp. 

```{r}
cambodia <- gapminder %>% 
  filter(country=="Cambodia") %>% 
  select(year, lifeExp)
cambodia
```

### 9. Select only the countries in Africa.
```{r}
africa <- gapminder %>% 
  filter(continent=="Africa")
africa
```

### 10. Create a new column called lifeExp_months that shows life expectancy in months. 

```{r}
lifeExp_months <- gapminder %>% 
  mutate(lifeExp_months = lifeExp/12) %>% 
  select(country, continent, year, lifeExp, lifeExp_months,everything())
lifeExp_months
```

 

