---
title: "R Tutorial 2"
subtitle: 'BIOL 4994/4991'
author: "Ariana Negroni Santiago"
date: "Last compiled on `r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

# Instructions
- This assignment consists of 10 questions, each worth 10 points.
- Write your answers in R code chunks whenever applicable.
- Make sure your code runs without errors. Include comments if necessary.
- For questions about chunk optins, experiment with the options and write down your observations.
- Submit the assignment on your personal webpages using the HTML file exported/knit from the .Rmd. Do not copy output screenshots unless requested.


### Using functions
1. Convert the built-in dataset BOD to a list and print the list. 

```{r}
BOD_df <- as.data.frame(BOD)
# BOD (Biochemical Oxygen Demand) is pre-defined Vector in R.
BOD_df
# Data Frame → List 
list_from_df <- as.list(BOD_df)
list_from_df
```

### Converting matrix into DataFrame
2. Convert the following data frame into a data frame and print the matrix.

```{r}
# Data frame 1
df1=data.frame(
  "Name"=c("a","b","c","d"),
  "Age"=c(12,34,23,67),
  "BMI"=c(22,12,10,11),
  "Country"=c("Malaysia","India","Spain","England"))
print(df1)
class(df1)
# Data Frame → Matrix 
matrix_from_df <- as.matrix(df1)
matrix_from_df
```

### Accessing 1st & 2nd rows
3. Create and print data frame

```{r}
# Data frame 2
df=data.frame(
  A=c("Raju","Kumar","Chandru","Deepak","Raina", "Dhoni", "Hema", "Vandana", "Bela","Anand" ),
  B=c(12,34,23,67,23,43,23,38,34,12),
  C=c("M","M","M","M","M","M","F","F","F","M"),
  D=c("Malaysia","India","Spain","England", "Malaysia", "Malaysia", "India", "Egypt", "Italy", "Peru"))
names(df)<-c("Name", "Age", "Gender","Country" )
print(df)
class(df)
```
4. Create a subset of the df dataset that includes only the first and second rows. Print the subset.
```{r}
# Subset of previous Data frame 2
subset_df<-df[c(1,2), ] # first and second row
subset_df
```

### Sorting the dataframe
5. Sort the df from Q3 by the Age column in ascending order. Print the sorted data frame. 

```{r}
#Sorted data frame 2 by age
df[order(df$Age), ]

```

### Adding a new column
6. Add a new column called Score to the df from Q3 with the following values: 85, 90, 78, 88, 90, 92, 80, 90, 87, 100. Print the updated data frame. 

```{r}
#New data frame 2 with new column
dfscore <- df
dfscore$Score <- c(85, 90, 78, 88, 90, 92, 80, 90, 87, 100)
dfscore
```

### Filtering rows with a condition
7. From the df in Q3, create a subset where Age is greater than 30. Print the subset.

```{r}
#Subset of data frame 2 with age greater than 30
df_subset2 <- subset(df, Age > 30) 
df_subset2
```

### Renaming columns
8. Rename the columns of df from Q3 as Person, Years, Gender, and Nation. Print the updated data frame.

```{r}
#Data frame 2 with new columns name
df_newcolumns_names <- df
colnames(df_newcolumns_names) <- c("Person", "Years", "Gender", "Nation")
df_newcolumns_names
```

### Selecting multiple conditions
9. From the df in Q2, select rows where Age is greater than 20 and BMI is less than 15. Print the subset.

```{r}
# Data frame 1 subset 
subset_df1 <- subset(df1, Age > 20 & BMI < 15)
subset_df1
```

### Summarizing a column
10. Calculate the mean of the Age column from df in Q2. Print the result. 

```{r}
# Mean of age from Data frame 1
mean_df1 <- mean(df1$Age)
mean_df1
```
