---
title: "R Tutorial 5 "
subtitle: 'BIOL 4994/4991'
author: "Ariana Negroni Santiago"
date: "Last compiled on `r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

## General instructions
- Make sure that all your R code is visible in your submitted document. I need to see the code for all ggplots you create.   
- We will be using data from the article: Curtis et al., 2012, Genomic and Transcriptomic Architecture of Breast Tumor. - I am giving you the initial code, the basics to start building a ggplot of Tumor Size vs Type of Breast Surgery.    
- Be sure to follow R syntax carefully and include all plots requested in the assignment.    

#### Load libraries: 
- readr, ggplot2 and janitor

```{r}
library(readr)
library(ggplot2)
library(janitor)
```

#### Load data:

```{r}
metabric <- read.csv("brca_metabric_clinical_data.csv") %>%
  clean_names()
head(metabric[, 1:5]) 
```

#### Basic ggplot:
```{r, warning= FALSE}
ggplot(metabric, aes(x = type_of_breast_surgery,
                     y = tumor_size,)) +
  geom_boxplot() 
```


### Question
##### Choose at least three modifications you think will improve the plot and make it more flexible and creative.
- Modify the X and Y axis titles.
```{r, warning= FALSE}
ggplot(metabric, aes(x = type_of_breast_surgery,
                     y = tumor_size,)) +
  geom_boxplot() +
  labs(title = "Tumor size per Breast Surgery",
       x = "Type of Breast Surgery",
       y = "Tumor Size") +
  theme(plot.title = element_text(hjust = 0.5))
```

- Change the color of the plot (using fill or color).
```{r, warning= FALSE}
ggplot(metabric, aes(x = type_of_breast_surgery,
                     y = tumor_size)) +
  geom_boxplot(fill = "orange") +
  labs(title = "Tumor Size per Breast Surgery",
       x = "Type of Breast Surgery",
       y = "Tumor Size") +
  theme(plot.title = element_text(hjust = 0.5))
```

- Change the background/theme of the plot.
```{r, warning= FALSE}
ggplot(metabric, aes(x = type_of_breast_surgery,
                     y = tumor_size)) +
  geom_boxplot(fill = "orange") +
  labs(title = "Tumor Size per Breast Surgery",
       x = "Type of Breast Surgery",
       y = "Tumor Size") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```



