---
title: "R Tutorial 4 "
subtitle: 'BIOL 4994/4991'
author: "Ariana Negroni Santiago"
date: "Last compiled on `r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---

## Instructions
- This assignment consists of uploading a plot and a brief paragraph (~250 words) summarizing your findings.
- In your paragraph, include the background of the data, what you did, how you did it, and what you found. 
- Submit your HTML file exported/knit from the .Rmd. Do not submit screenshots unless requested. 
- Your paragraph should briefly summarize your workflow and findings. For example: I analyzed the data of tyre performance. I visualized it using ggplot() and then ran a one-way ANOVA. We checked for normality of residuals and found that the residuals were approximately normally distributed. I ran a Tukey post-hoc test. I found that the high-performance tyres were Brand X, and the lower-performance tyres were Brand Y and Z.


```{r, Warnings=FALSE}
setwd("~/Pre-medica/Quinto año/R/Intro_R/Intro-R/Rtutorials")
library(ggplot2)
library(dplyr)
library(car)
tyre <- read.csv("tyre.csv")
```

```{r}
color <- c("orange", "purple", "lightgreen", "darkred")
ggplot(tyre, aes(x = Brands, y = Mileage)) + 
  geom_boxplot(aes(fill = Brands)) +
# labels
  labs(x = "Gomas", y = "Kilometers",
       title = "Gomas en Puerto Rico") +
# themes
  theme_bw() +  
  theme(plot.title = element_text(size = 20, 
                                      face ="bold", 
                                      hjust = 0.5,
                                      color = "darkred")) +
  theme(axis.title.y = element_text(size = 14,
                                    face = "plain"),
        axis.text.y = element_text(size = 14,
                                   color = "black")) +
  theme(axis.title.x = element_text(size = 14,
                                    face = "plain"),
        axis.text.x = element_text(size = 14,
                                   color = "black")) +
  theme(legend.title = element_text(size = 18,
                                    face = "bold")) +
  theme(legend.text = element_text(size = 14)) +
  theme(legend.position = 'none') +
  ylim(20,50)
# theme_minimal()
```

```{r, Warning=FALSE}
#ANOVA one way
mod <- aov(Mileage ~ Brands, data = tyre)
summary(mod)

resid_anova <- residuals(mod)
resid_anova

shapiro.test(resid_anova)

leveneTest(Mileage ~ Brands, data = tyre)

TukeyHSD(mod)
```

